Resumé title

### 2017-06-29 paper/coverletter.tex
Tweak counts

The document has been formatted with the \LaTeX\ article class.
The summary is 286 words long, and the main text has $\approx 1424$ words,
29 references,
and two single-panel figures and one table, which should fit the page limit
of a Nature Letter.
We also include six extended data figures that will help interested readers
get the full context, as well as supplementary material discussing several
aspects of the main text in more detail.

>>>>

The document has been formatted with the \LaTeX\ article class.
The summary is 286 words long, and the main text has $\approx 1467$ words, 29
references, two single-panel figures and one table, which should fit the page
limit of a Nature Letter.
We also include six extended data figures that will help interested readers
get the full context, as well as supplementary material discussing several
aspects of the main text in more detail.
